---
title: "Grand Anse, Haitii - Saftey Net Program"
author: "Noimot Bakare"
date: "3/8/2021"
output: beamer_presentation
---

```{r Libraries, include=FALSE}
library(rtrim)
library(Hmisc)
library(csv)
library(foreign)
library(stringr)              
library(psych)

library(collapse)
##########################Summary Stats#############################
library(data.table)
library(stats)
library(DataExplorer)
library(reporttools)
library(reshape)
library(freqdist)
library(knitr)
library(rmarkdown)
library(tinytex)
library(markdown)
library(summarytools)
library(kableExtra)
library(haven)
library(survey)
library(srvyr)
library(ggplot2)

#########################Graphics and visualization#################
# library(plotly)
# library(gganimate)
# library(maptools)
# library(maps)
# library(ggmap)   
##########################Data Wrangling##############################
library(stringr)
library(tidyverse)
#library(tidyr)
#library(plyr)
library(dplyr)
library(devtools) 
library(pastecs)
library(janitor)
#########################3
library(AER)
library(sandwich)
library(readxl)
library(foreign)
library(apa)
# options(scipen=999)

###calling libraries for graphs
#library('ggplot2')
library('scales')     # for scale_y_continuous(label = percent)
library('ggthemes')   # for scale_fill_few('medium')
#library(viridis)  #Purple green yellow collor palett
library('ztable')     # format tables for reporting
library(stargazer)
library(texreg)
library(fastDummies)

library(readxl)
library(tidyverse)
library(haven)
library(gt)
library(janitor)
library(FSA)

grand_anse_dataforDRM_nb <- read.csv("~/Dropbox/grand_anse_data_nb.csv")

```

##  HDVI - Haiti's Deprivation and Vulnerability Index 
**HDVI**

 - Consists of 20 indicators of living conditions 
 - Across 7 dimensions of vulnerability
 - Is a  a number [0 <= HDVI <= 1] 
 - The higher the HDVI the higher the household deprivation
  

 
##  Household Classification 
  **Households are classified into 4 categories**
  
 - More Deprived
 - Mid Deprived
 - Less Deprived
 - Not Deprived


##  Objective: 
> Of the 7 vulnerabiilty measures, food vulnerability is the variable of interest, because food consumption is a good predictor of a househod well-being. 

> This analysis is the first stage in identifying the most vulnerable population in Grande Anse, Haiti. 

## Data: 
**Households were asked 3 series of questions regarding food security over the 4 weeks prior to the data collection/ survey interview period.**

1. Absence of Food - If HH members experienced absence of food due to lack of resources.

2. Hunnger - If HH members went to bed hungy because they could not eat sufficiently. 

3. Restricted Consumptioon - If HH members were forced to fast during an entire day becuase there was not enough food. 

**Possible Responses:**

1. never
2. sometimes 
3. Often
 

## Variables of Interest:

In the 4 weeks prior to the interview date:

 **Absence of Food**
- cat_hh_no_food_at_all1  
- cat_hh_no_food_at_all2
- cat_hh_no_food_at_all3

 **Forced to fast**
- cat_hh_day_no_food1,   
- cat_hh_day_no_food2
- cat_hh_day_no_food3

 **Went to bed hungry**
- cat_hh_bed_hungry1
- cat_hh_bed_hungry2
- cat_hh_bed_hungry3



```{r Data , include=FALSE}



# #Pulling in socialll rrefistry data 
# grand_anse <- read_excel("Dropbox/WB_GFDRR_STC/Grand_anse/grand_anse_dataforDRM_nb.xlsx")
# 

# grand_anse_dataforDRM_nb <- read_excel("Dropbox/WB_GFDRR_STC/Grand_anse/grand_anse_data_nb.xlsx")



Gran_Anse <- grand_anse_dataforDRM_nb %>%  select(commune, urban, hhsize, relation_to_hhh, haitisdeprivationsandvulnerabili, mi_vulnerable, moins_vulnerable, non_vulnerable, plus_vulnerable, 
cat_hh_no_food_at_all1,                      
cat_hh_no_food_at_all2,
cat_hh_no_food_at_all3,
cat_hh_day_no_food1,     
cat_hh_day_no_food2,
cat_hh_day_no_food3,
cat_hh_bed_hungry1,
cat_hh_bed_hungry2, 
cat_hh_bed_hungry3)

Gran_Anse_1 <- Gran_Anse %>%   na.omit(Gran_Anse)

Gran_Anse_1$HDVI <- Gran_Anse_1$haitisdeprivationsandvulnerabili

Gran_Anse_1$no_vulnerability<- Gran_Anse_1$non_vulnerable
Gran_Anse_1$less_vulnerability<- Gran_Anse_1$moins_vulnerable 
Gran_Anse_1$mid_vulnerability<- Gran_Anse_1$mi_vulnerable 
Gran_Anse_1$more_vulnerability<- Gran_Anse_1$plus_vulnerable 
 
Gran_Anse_1 <- Gran_Anse_1 %>% select(-mi_vulnerable,-non_vulnerable,-moins_vulnerable, -plus_vulnerable, -haitisdeprivationsandvulnerabili )
Gran_Anse_1<- as.data.frame(Gran_Anse_1)

#Absence of Food 
Gran_Anse_1$cat_hh_no_food_at_all1<- as.factor(Gran_Anse_1$cat_hh_no_food_at_all1)

Gran_Anse_1$cat_hh_no_food_at_all2<- as.factor(Gran_Anse_1$cat_hh_no_food_at_all2)

Gran_Anse_1$cat_hh_no_food_at_all3<- as.factor(Gran_Anse_1$cat_hh_no_food_at_all3)


#FAST
Gran_Anse_1$cat_hh_day_no_food1<- as.factor(Gran_Anse_1$cat_hh_day_no_food1)

Gran_Anse_1$cat_hh_day_no_food2<- as.factor(Gran_Anse_1$cat_hh_day_no_food2)

Gran_Anse_1$cat_hh_day_no_food3<- as.factor(Gran_Anse_1$cat_hh_day_no_food3)

#Hunger
Gran_Anse_1$cat_hh_bed_hungry1<- as.factor(Gran_Anse_1$cat_hh_bed_hungry1)

Gran_Anse_1$cat_hh_bed_hungry2<- as.factor(Gran_Anse_1$cat_hh_bed_hungry2)

Gran_Anse_1$cat_hh_bed_hungry3<- as.factor(Gran_Anse_1$cat_hh_bed_hungry3)



#Mutating a single column 

Gran_Anse_1 <- Gran_Anse_1 %>%
  mutate(Bed_Hungery = case_when(
    cat_hh_bed_hungry1 %in% "1" ~ "Never",
    cat_hh_bed_hungry2 %in% "1" ~ "Sometimes",
    cat_hh_bed_hungry3 %in% "1" ~ "Often"
  ))

  Gran_Anse_1 <- Gran_Anse_1 %>%
  mutate(Bed_Hungery_depth = case_when(
    cat_hh_bed_hungry1 %in% "1" ~ "1",
    cat_hh_bed_hungry2 %in% "1" ~ "2",
    cat_hh_bed_hungry3 %in% "1" ~ "3"
  )) 
  
  
  
Gran_Anse_1 <- Gran_Anse_1 %>%
  mutate(Absence_Food = case_when(
    cat_hh_no_food_at_all1 %in% "1" ~ "Never",
    cat_hh_no_food_at_all2 %in% "1" ~ "Sometimes",
    cat_hh_no_food_at_all3 %in% "1" ~ "Often"
  ))

Gran_Anse_1 <- Gran_Anse_1 %>%
  mutate(Absence_Food_depth = case_when(
    cat_hh_no_food_at_all1 %in% "1" ~ "1",
    cat_hh_no_food_at_all2 %in% "1" ~ "2",
    cat_hh_no_food_at_all3 %in% "1" ~ "3"
  )) 


Gran_Anse_1 <- Gran_Anse_1 %>%
  mutate(Restricted_Food = case_when(
    cat_hh_day_no_food1 %in% "1" ~ "Never",
    cat_hh_day_no_food2 %in% "1" ~ "Sometimes",
    cat_hh_day_no_food3 %in% "1" ~ "Often"
  ))

Gran_Anse_1 <- Gran_Anse_1 %>%
  mutate(Restricted_Food_depth = case_when(
    cat_hh_day_no_food1 %in% "1" ~ "1",
    cat_hh_day_no_food2 %in% "1" ~ "2",
    cat_hh_day_no_food3 %in% "1" ~ "3"
  )) 


```

## Summary Statistics

```{r Summary Stat, echo=FALSE}

stargazer(Gran_Anse_1 , type ='text', title="Summary Statistics", align=TRUE, column.sep.width = ".8pt", single.row = TRUE)

#stargazer(Gran_Anse_1)
# knitr::kable(Gran_Anse_1, caption = "Summary Statistics")
```



## Summary Statistics

```{r Summary Stat2, echo=FALSE}

stargazer(Gran_Anse_1) 

#stargazer(Gran_Anse_1)
# knitr::kable(Gran_Anse_1, caption = "Summary Statistics")
```



```{r Summary Stat3, echo=FALSE}

kable(Gran_Anse_1)

#stargazer(Gran_Anse_1)
# knitr::kable(Gran_Anse_1, caption = "Summary Statistics")
```
```{r Plots, eval=FALSE, include=FALSE}
# #Absence of Food
# 
# cdplot(cat_hh_no_food_at_all1 ~ HDVI, Gran_Anse_1, col=c("cornflowerblue", "orange"), main="Households that never experienced absence of food")
# 

```

## Absence of food - Often

```{r Plots1, echo=FALSE}
cdplot(cat_hh_no_food_at_all3 ~ HDVI, Gran_Anse_1, col=c("cornflowerblue", "orange"), main="Households that often experienced absence of food")

```

## Absence of food - Sometimes 

```{r Plots2, echo=FALSE}
 cdplot(cat_hh_no_food_at_all2 ~ HDVI, Gran_Anse_1, col=c("cornflowerblue", "orange"), main="Households that sometimes experienced absence of food") 

```

## Forced to Fast - Often

```{r Plots3, echo=FALSE}
cdplot(cat_hh_day_no_food3 ~ HDVI, Gran_Anse_1, col= c("lightblue","darkblue"), main="Households that were often forced to fast due to lack of food") 

```


## Forced to Fast - Sometimes 

```{r Plots4, echo=FALSE}

cdplot(cat_hh_day_no_food2 ~ HDVI, Gran_Anse_1,  col= c("lightblue","darkblue"), main="Households that were sometimes forced to fast due to lack of food") 

```

## Went to bed Hungry - Often

```{r Plots5, echo=FALSE}


cdplot(cat_hh_bed_hungry3 ~ HDVI, Gran_Anse_1, col= c("lightblue","darkblue"), main="Household that often go to bed hungry") 
 
```


## Went to bed Hungry - Sometimes
```{r Plots6, echo=FALSE}

cdplot(cat_hh_bed_hungry2 ~ HDVI, Gran_Anse_1, col= c("lightblue","darkblue"), main="Household that sometimes go to bed hungry") 
```


## Population distribution - Gone to bed hungry 
```{r Plots7, echo=FALSE}

  


ggplot(Gran_Anse_1, aes(x = HDVI)) +  
  geom_density(aes(group = Bed_Hungery, 
                   colour = Bed_Hungery, 
                   fill = Bed_Hungery),
               alpha = 0.2) 


```

## Population distribution - Absence of Food 
```{r Plots 8, echo=FALSE}



ggplot(Gran_Anse_1, aes(x = HDVI)) +  
  geom_density(aes(group = Absence_Food, 
                   colour = Absence_Food, 
                   fill = Absence_Food),
               alpha = 0.2)


```


## Population distribution - Restricted Consumption
```{r Plots 9, echo=FALSE}


ggplot(Gran_Anse_1, aes(x = HDVI)) +  
  geom_density(aes(group = Restricted_Food, 
                   colour = Restricted_Food, 
                   fill = Restricted_Food),
               alpha = 0.2) 

```


## Population distribution - Restricted Consumption
```{r Plots 10, echo=FALSE}
library(ggplot2)
library(grid)
library(gridExtra)

##Import data
df<- read.csv("D:\\R\\SF_Question.csv")

##Draw individual plots
#the lower panel
p1<- ggplot(Gran_Anse_1, aes(HDVI, Restricted_Food)) + geom_line() + scale_y_reverse() + labs(x="AGE") + scale_x_continuous(breaks = seq(1000,2000,200), limits = c(1000,2000))
#the upper panel
p2<- ggplot(df, aes(TIME2, V2)) + geom_line() + labs(x=NULL) + scale_x_continuous(breaks = seq(1000,2000,200), limits = c(1000,2000)) + theme(axis.text.x=element_blank())
